The finite representation property for some reducts of relation algebras

### 2021-04-17 frp-paper/Paper.tex
update refs

The following proposition is a version of \cite[Proposition 7.24]{hirsch2002relation} and the right-to-left part is proved using K\"{o}nig's lemma \cite[Exercise 5.6.3]{hodges1997shorter}.

@@

  Suppose $\exists$ has a winning strategy has a winning strategy in $\mathcal{G}_m(\mathcal{A})$ for $m < \omega$. The proof scheme is the same as for relation or cylindric algebras, so we provide the following sketch. In particular, we have the following proof that may be proved using \strokeL o\'s's Theorem similarly to.

@@

  Consider $\mathcal{B}$, a countable elementary equivalent subalgbera of $\Pi_{U} \mathcal{A}$ that exists by the downward L\"{o}wenheim-Skolem theorem.
  We construct the following elementary chain inxeded over $\omega$:
  \begin{center}
    $\mathcal{B}_0 \preceq \mathcal{B}_1 \preceq \dots \mathcal{B}_i \preceq\mathcal{B}_{i + 1} \preceq \dots (\preceq \Pi_{U} \mathcal{A})$.
  \end{center}
  Let us put $\mathcal{B}_0 := \mathcal{B}$.
  Suppose the initial segment $\mathcal{B}_0 \preceq \mathcal{B}_1 \preceq \dots \mathcal{B}_i$ has been already constructed. Let us constuct $\mathcal{B}_{i + 1}$.

@@

  Let us put $\mathfrak{B} = \bigcup \limits_{i < \omega} \mathcal{B}_i$. Note that $\mathfrak{B}$ is countable. By Tarksi-Vaught elementary chain union theorem, for each $i < \omega$ $\mathcal{B}_i \preceq \mathfrak{B}$. Therefore, $\mathfrak{B} \equiv \Pi_{U} \mathcal{A}$. On the other hand, $\mathcal{A} \equiv \Pi_{U} \mathcal{A}$.
  Moreover, $\mathfrak{B}$ is representable and $\mathfrak{B} \equiv \mathcal{A}$.
\end{proof}

>>>>

The following proposition is a version of \cite[Proposition 7.24]{hirsch2002relation} and the right-to-left part is proved using K\"{o}nig's lemma \cite[Exercise 5.6.5]{hodges1993model}.

@@

  Suppose $\exists$ has a winning strategy has a winning strategy in $\mathcal{G}_m(\mathcal{A})$ for $m < \omega$. The proof scheme is the same as for relation (see \cite[Lemma 19]{hirsch1997complete}) or cylindric algebras (see \cite[Corollary 3.3.5]{hirsch2013completions}), so we provide the following sketch. In particular, we have the following proof that may be proved using \strokeL o\'s's theorem (see \cite[Theorem 9.5.1]{hodges1993model}) similarly to.

@@

  Consider $\mathcal{B}$, a countable elementary equivalent subalgbera of $\Pi_{U} \mathcal{A}$ that exists by the downward L\"{o}wenheim-Skolem theorem, see \cite[Corollary 3.1.5]{hodges1993model}.
  We construct the following elementary chain inxeded over $\omega$:
  \begin{center}
    $\mathcal{B}_0 \preceq \mathcal{B}_1 \preceq \dots \mathcal{B}_i \preceq\mathcal{B}_{i + 1} \preceq \dots (\preceq \Pi_{U} \mathcal{A})$.
  \end{center}
  Let us put $\mathcal{B}_0 := \mathcal{B}$.
  Suppose the initial segment $\mathcal{B}_0 \preceq \mathcal{B}_1 \preceq \dots \mathcal{B}_i$ has been already constructed. Let us constuct $\mathcal{B}_{i + 1}$.

@@

  Let us put $\mathfrak{B} = \bigcup \limits_{i < \omega} \mathcal{B}_i$. Note that $\mathfrak{B}$ is countable. By Tarksi-Vaught elementary chain union theorem (see \cite[Theorem 2.5.2]{hodges1993model}), for each $i < \omega$ $\mathcal{B}_i \preceq \mathfrak{B}$. Therefore, $\mathfrak{B} \equiv \Pi_{U} \mathcal{A}$.
  On the other hand, $\mathcal{A} \equiv \Pi_{U} \mathcal{A}$ (see \cite[Corollary 9.5.2]{hodges1993model}).
  Moreover, $\mathfrak{B}$ is representable and $\mathfrak{B} \equiv \mathcal{A}$.
\end{proof}
